Keep your Laziness in Check

### 2018-02-11 paper/main.tex
backup

However, Okasaki cleverly improved upon this design using lazy lists
that both incrementally performs the reversal of the back list, and
incrementally appends the reversal of the back list onto the front
list ~\cite{Okasaki95simpleand}. Okasaki's queue relies on the
following \lk{rotate} function to incrementally reverse and append the
back list.
\begin{inlinecode}
rotate []    back acc = (head back)  : acc
rotate front back acc = (head front) : rest
  where rest = rotate (tail front) (tail back) ((head back) : acc)
\end{inlinecode}
If we computed the expression \lk{rotate front back []}, its value
will be equivalent to \lk{front ++ (reverse back)}. However, the
function \lk{rotate} is much lazier than the naive reverse and append
operation. The function \lk{reverse} has to evaluate the entire
structure of the back list, which is not incremental. On the other
hand, the function \lk{rotate} produces a list immediately, and packs
the rest of the computation into the lazy list \lk{rest}.

@@

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
We are grateful to
%
Matt Parsons,
Matthew Weaver,
Jennifer Paykin,
Antal Spector-Zabusky,
and the Penn PLClub 
for their useful comments. 
This material is based upon work supported by the
\grantsponsor{GS100000001}{National Science
  Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
No.~\grantnum{GS100000001}{1421243} ({\em Random Testing for Language
Design}), Grant No.~\grantnum{GS100000001}{1521523} ({\em Expeditions
in Computing: The Science of Deep Specification}), and \leo{Kenny,
Hengchu, ask for grant numbers names} Any opinions, findings, and
conclusions or recommendations expressed in this material are those of
the author and do not necessarily reflect the views of the National
Science Foundation.

>>>>

However, Okasaki cleverly improved upon this design using lazy lists
that both incrementally performs the reversal of the back list, and
incrementally appends the reversal of the back list onto the front
list ~\cite{Okasaki95simpleand}. Okasaki's queue relies on the
following \lk{rotate} function to incrementally reverse and append the
back list.
\begin{inlinecode}
rotate :: [a] -> [a] -> [a] -> [a]
rotate      []       []  as =                       as
rotate      []  (b : bs) as =     rotate [] bs (b : as)
rotate (f : fs)      []  as = f : rotate fs []      as
rotate (f : fs) (b : bs) as = f : rotate fs bs (b : as)
\end{inlinecode}
If we computed the expression \lk{rotate front back []}, its value
will be equivalent to \lk{front ++ (reverse back)}. However, the
function \lk{rotate} is much lazier than the naive reverse and append
operation. The function \lk{reverse} has to evaluate the entire
structure of the back list, which is not incremental. On the other
hand, the function \lk{rotate} produces a list immediately, and packs
the rest of the computation into the lazy list \lk{rest}.

@@

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
We are grateful to
%
José Manuel Calderón Trilla,
Matt Parsons,
Stephanie Weirich,
Jennifer Paykin,
Robert Rand,
Antal Spector-Zabusky,
Matthew Weaver,
and the Penn PLClub
for their useful comments.
This material is based upon work supported by the
\grantsponsor{GS100000001}{National Science
  Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
No.~\grantnum{GS100000001}{1421243} ({\em Random Testing for Language
Design}), Grant No.~\grantnum{GS100000001}{1521523} ({\em Expeditions
in Computing: The Science of Deep Specification}), and \leo{Kenny,
Hengchu, ask for grant numbers names} Any opinions, findings, and
conclusions or recommendations expressed in this material are those of
the author and do not necessarily reflect the views of the National
Science Foundation.
